\documentclass[16pt]{article}

\usepackage{report}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[english, russian]{babel}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{mathtools}
\usepackage{minted}
\usepackage{graphicx}
\graphicspath{ {./figs/} }

\setcitestyle{aysep={,}}

\title{Lab \textnumero 7 "Controllability and Observability"}

\author{
Student \\
Kirill Lalayants\\
R33352\\
336700\\
\\
Teacher\\
Pashenko A.V. \\
\\
\\
\\
Faculty of Control Systems and Robotics\\
\\
ITMO\\
}

% Uncomment to remove the date
\date{February 9, 2024}

% Uncomment to override the `A preprint' in the header
\renewcommand{\headeright}{Lab \textnumero 7 "Controllability and Observability"}
\renewcommand{\undertitle}{Report}
\renewcommand{\shorttitle}{}


\begin{document}
\maketitle
\newpage
\tableofcontents
\thispagestyle{empty}

\newpage
\setcounter{page}{1}
\section{Introduction}
\subsection{Objective}
This work aims to study the controllability and observability of systems.


\subsubsection{Software Implementation}
The source code can be found on \href{https://github.com/lalayants/control-theory-itmo-2023-2024}{GitHub repository}.
\newpage
\section{Main Part}
\input{src/n1}

\newpage
\input{src/n2}

\newpage
\input{src/n3}


\newpage
\input{src/n4}

\newpage
\section{Conclusion}
In this work, the controllability and observability of systems have been studied.
\subsection{Summary}
\begin{enumerate}
   \item Fully controllable systems have been investigated. 
   \item Various controllability criteria have been tested. 
   \item Partially controllable systems have been examined, and methods for checking state membership in the controllable subspace have been verified. 
   \item Fully observable systems have been explored. 
   \item Various observability criteria have been checked. 
   \item Partially observable systems have been studied, and methods for verifying the uniqueness of obtained initial conditions have been confirmed. 
\end{enumerate}

\end{document}
